PANCHANGE_analysis

### 2020-08-25 PANCHANGE_analysis.Rmd
add age category chi square

## age_category_full
```{r Inspect age_category_full}
dat.raw %>%
  freq(age_category_full)

dat.raw %>%
  freq(age_category_full_numeric)
```

```{r Collapse age_category_full}
dat.raw <- dat.raw %>%
  mutate(age_category_collapsed_numeric =
           case_when(
             age_category_full_numeric == 1 ~ 0,
             age_category_full_numeric == 2 ~ 1,
             age_category_full_numeric == 3 ~ 2,
             age_category_full_numeric == 4 ~ 3,
             age_category_full_numeric == 5 ~ 4,
             age_category_full_numeric == 6 ~ 5,
             age_category_full_numeric == 7 ~ 6,
             age_category_full_numeric == 8 ~ 7,
             age_category_full_numeric == 9 ~ 9,
             age_category_full_numeric == 10 ~ 9,
             age_category_full_numeric == 11 ~ 9,
             age_category_full_numeric == 12 ~ 9,
             age_category_full_numeric == 13 ~ 9

@@

+++ADD CHUNK FOR AGE CATEGORIES HERE
```{r Age categories}
dat %>%
  freq(age_category_full)
```

+++ADD CHUNK FOR AGE CATEGORIES HERE
```{r Age categories by Sample}
dat %>%
  group_by(Sample) %>%
  count(age_category_full, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

@@

Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
```{r}
model1 <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender + age_category_full + Ethnicity + time_diff_sign_up_coping,
  data = dat)

@@

Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
```{r}
model1 <- lm(
  formula = pcl.diff_score_base_prepan ~ Disorder_hierarchical + Gender + age_category_full + Ethnicity + time_diff_sign_up_coping,
  data = dat)

>>>>

## age_category
```{r Inspect age_category}
dat.raw %>%
  freq(age_category)

dat.raw %>%
  freq(age_category_numeric)
```

```{r Collapse age_category}
dat.raw <- dat.raw %>%
  mutate(age_category_collapsed_numeric =
           case_when(
             age_category_numeric == 1 ~ 0,
             age_category_numeric == 2 ~ 1,
             age_category_numeric == 3 ~ 2,
             age_category_numeric == 4 ~ 3,
             age_category_numeric == 5 ~ 4,
             age_category_numeric == 6 ~ 5,
             age_category_numeric == 7 ~ 6,
             age_category_numeric == 8 ~ 7,
             age_category_numeric == 9 ~ 8,
             age_category_numeric == 10 ~ 8,
             age_category_numeric == 11 ~ 8,
             age_category_numeric == 12 ~ 8,
             age_category_numeric == 13 ~ 8

@@

+++ADD CHUNK FOR AGE CATEGORIES HERE
```{r Age categories}
dat %>%
  freq(age_category)
```

+++ADD CHUNK FOR AGE CATEGORIES HERE
```{r Age categories by Sample}
dat %>%
  group_by(Sample) %>%
  count(age_category, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r Gender per Sample count cross table}
dat %>%
  count(age_category, Sample) %>%
  spread(key = Sample, value = n)
```

```{r Gender per Sample count cross table chi square test}
dat %>%
  count(age_category, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-age_category) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0))
    ) %>%
  chisq.test() %>%
  glance()
```

@@

Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
```{r}
model1 <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender + age_category + Ethnicity + time_diff_sign_up_coping,
  data = dat)

@@

Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
```{r}
model1 <- lm(
  formula = pcl.diff_score_base_prepan ~ Disorder_hierarchical + Gender + age_category + Ethnicity + time_diff_sign_up_coping,
  data = dat)
